\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-06 coqimpl.tex
Reconsiderate phrase of "Extensible"

\textbf{Special Fields: Extensible Inductive Type and Defining Recursor.}

>>>>

\textbf{Special Fields: ``Extensible'' Inductive Type and Defining Recursor.}

Even though in our metatheory there is no notion of extensible inductive type, but in our implementation we have the syntax of extensible inductive type.

### 2022-06-06 standardmodel.tex
Reconsiderate phrase of "Extensible"

% We omit the model here for extensible inductive type and inheritance judgement because they require inductive facility in meta-logic. 
We spell-out the model for extensible type and inheritance judgement here, and both of them require inductive facility in meta-logic. In set theory, that would be using \textit{Rule sets}~\citep{timany2017consistency,aczel1998relating}, but we are using Agda's Inductive facility instead. 
% In appendix we will use the native inductive notion from Agda to construct models. 
As expected, we use an inductive type with the constructor from W-type to model our extensible inductive type, and the recursor for the inductive type is directly modelling the recursor for our extensible inductive type. For inheritance judgement, we inductively define an almost-identical syntactic structure as model, (but not a QIIT), and we inductively define meta-level substitution to implement the explicit substitution. We also define $inh$ operation by induction strictly following $\beta$-law. Basically both ideas are using the syntax of themselves in meta-logic to model, because its definition is pretty "well-founded". Most importantly, this doesn't affect our aim to model bottom type using empty set to derive consistency.

>>>>

% We omit the model here for inductive type and inheritance judgement because they require inductive facility in meta-logic. 
We spell-out the model for the inductive type and inheritance judgement here, and both of them require inductive facility in meta-logic. In set theory, that would be using \textit{Rule sets}~\citep{timany2017consistency,aczel1998relating}, but we are using Agda's Inductive facility instead. 
% In appendix we will use the native inductive notion from Agda to construct models. 
As expected, we use an inductive type in the meta-logic with the constructor from W-type to model our inductive type, and the recursor for the inductive type in the meta-logic is directly modelling the recursor for our inductive type in our theory. For inheritance judgement, we inductively define an almost-identical syntactic structure as model, (but not a QIIT), and we inductively define meta-level substitution to implement the explicit substitution. We also define $inh$ operation by induction strictly following $\beta$-law. Basically both ideas are using the syntax of themselves in meta-logic to model, because its definition is pretty "well-founded". Most importantly, this doesn't affect our aim to model bottom type using empty set to derive consistency.

### 2022-06-06 syntax.tex
Reconsiderate phrase of "Extensible"

We have two kinds of signatures, one for extensible inductive type, the other for linkages.

@@

Recall in W-type \citep{martin1982constructive}, a pair of type $x : A \vdash B(x)$ decides a W-type. For simplicity,  we use a list of pairs of such $A, B$ as the signature for a given inductive type. Doing so, all the constructors will have a fixed form \mintinline{agda}{cstrᵢ : (x : Aᵢ) → (Bᵢ x → W) → W}.
Of course we need to put an eye on the substitution law for each piece of the syntax. Here $\bW \sigma$ is a large singleton type \cite{stone2000}, and it only has one "element", the inductive type itself, inside. We formulate in this cumbersome way because we want to have inductive type to be an abstract field element at the same time exposing the constructors for later \textit{pattern-matching coverage checking} (i.e. if an inductive type as field element has type $\cU$, then no information about the inductive type is exposed).\YZ{What is the distinction of 'W T' vs 'El (W T)'?}\EDJreply{(W T) is a term inside the type universe, El (W T) is really a type. They are basically the same thing but (W T) cannot be at the type position in a judgement, i.e. k |- q : (W T) is not allowed, we only have k |- q : El (W T). This is kind of standard notation (at least in both Sterling and Kaposi) so I will avoid explaining in the main text if you think ok?}\YZreply{I think explanation is warranted; readers unfamiliar with that line of work may find it confusing. BTW, is the elimination rule for "El (W T)" omitted?}

>>>>

We have two kinds of signatures, one for inductive type, the other for linkages.

@@

Recall in W-type \citep{martin1982constructive}, a pair of type $x : A \vdash B(x)$ decides a W-type. To simulate extensible inductive type, we have to equip our inductive type with multiple constructors, and for simplicity, each constructor has a fixed form \mintinline{agda}{cstrᵢ : (x : Aᵢ) → (Bᵢ x → W) → W}. Thus we use a list of pairs of such $A_i, B_i$ as the signature for a given inductive type.

Of course we need to put an eye on the substitution law for each piece of the syntax. Here $\bW \sigma$ is a large singleton type \cite{stone2000}, and it only has one "element", the inductive type itself, inside. We formulate in this cumbersome way because we want to have inductive type to be an abstract field element at the same time exposing the constructors for later \textit{pattern-matching coverage checking} (i.e. if an inductive type as field element has type $\cU$, then no information about the inductive type is exposed).\YZ{What is the distinction of 'W T' vs 'El (W T)'?}\EDJreply{(W T) is a term inside the type universe, El (W T) is really a type. They are basically the same thing but (W T) cannot be at the type position in a judgement, i.e. k |- q : (W T) is not allowed, we only have k |- q : El (W T). This is kind of standard notation (at least in both Sterling and Kaposi) so I will avoid explaining in the main text if you think ok?}\YZreply{I think explanation is warranted; readers unfamiliar with that line of work may find it confusing. BTW, is the elimination rule for "El (W T)" omitted?}
